Using DIT to simplify the DBF feasibility test

### 2013-07-19 dit-paper.tex
minor changes renamed baruah pdf

\newcommand{\dbf}[1]{\operatorname{dbf}(#1)}

@@

 Mathematically,
 $$\dbf{t} = \max_{\{\forall \: t_1, t_2 \mid t_2 - t_1 = t \: \wedge \: 0
 \leqslant t_1 \leqslant t_2\}} \sum_{i=1}^n C_i \cdot h_i(t_1, t_2)$$ where
 $h_i(t_1, t_2)$ is the number of jobs of task $i$ whose arrival and deadline are in (non-strict) the interval $[t_1, t_2]$.
\end{definition}

@@

In the sequel a closed form expression of the DBF is given in the synchronous
case. Intuitively, in this case it will be a step-function whose increases will
occur at every job deadline, with the increase being equal to the execution time of the corresponding job.\\

Starting from the definition, it remains to find a method to compute the values
of $h_i(0, t)$ (noted $h_i(t)$ from now on). In the synchronous case, these
values can be obtained as $$h_i(t) = \operatorname{max} \; \{ k \in \mathbb{N} :
k T_i  + D_i \leq t \} + 1 $$ Indeed, $k = 0$ correspond to the first task, $k =
1$ to the second task, etc. The maximal value of $k$ can be explicitly stated by rearranging the condition:
$$k T_i + D_i \leq t$$
$$\iff 0 \leq k \leq \lfloor \frac{t - D_i}{T_i} \rfloor$$
The highest value is $k = \lfloor \frac{t - D_i}{T_i} \rfloor$. If this value is negative, it means that no job of task $\tau_i$ respects the condition, i.e. $h_i(t) = 0$. Else, we can inject it directly and obtain $h_i(t) = \lfloor \frac{t - D_i}{T_i} \rfloor + 1$\\

This is generalized by the final definition of $h_i(t)$: $$h_i(t) = \operatorname{max} \{ 0, \lfloor \frac{t - D_i}{T_i} \rfloor + 1 \}$$

With this result, a closed form of the DBF function in the synchronous case is obtained $$\dbf{t} = \sum_{i=1}^{n} \operatorname{max} \{ 0, \lfloor \frac{t - D_i}{T_i} \rfloor + 1 \} \, C_i$$

@@

In \cite{baruah1990algorithms}, the authors show that the DBF can be used to derive the following feasibility condition for EDF\footnote{And thus, EDF being optimal, for all optimal schedulers} on sporadic task sets. An adapted proof is given here.

\begin{theorem}
$$\text{$(\tau_1, ..., \tau_n)$ is feasible} \iff \dbf{t} \leq t \; \forall t$$
\end{theorem}

\begin{proof}
	We first show that the condition is \emph{necessary}. Indeed, if the condition is not fulfilled (i.e. $\exists t^* \; s.t. \; \dbf{t^*} > t^*$), it means that in an interval of $t^*$ time units, the total execution time of the jobs whose arrival and deadline occurs within the interval is superior to $t^*$. The system is thus not feasible if the condition is not fulfilled.\\

>>>>

\renewcommand{\arraystretch}{1.4}
\newcommand{\dbf}[1]{\operatorname{dbf}(#1)}

@@

	Mathematically,
	\[ 
		\dbf{t} = \max_{\{\forall \: t_1, t_2 \mid t_2 - t_1 = t \: \wedge \: 0
		\leqslant t_1 \leqslant t_2\}} \sum_{i=1}^n C_i \cdot h_i(t_1, t_2) 
	\] 
	where $h_i(t_1, t_2)$ is the number of jobs of task $i$ whose arrival and
	deadline are in (non-strict) the interval $[t_1, t_2]$.
\end{definition}

@@

In the sequel a closed form expression of the DBF is given in the synchronous
case. Intuitively, in this case it will be a step-function which increases will
occur at every job deadline, with the increase being equal to the execution time of the corresponding job.\\

Starting from the definition, it remains to find a method to compute the values
of $h_i(0, t)$ (noted $h_i(t)$ from now on). In the synchronous case, these
values can be obtained as 
\[
	h_i(t) = \operatorname{max} \; \{ k \in \mathbb{N} :
	k T_i  + D_i \leq t \} + 1
\]
Indeed, $k = 0$ corresponds to the first task, $k = 1$ to the second task, etc.
The maximal value of $k$ can be explicitly stated by rearranging the condition:
\[
	\begin{array}{c}
		k T_i + D_i \leq t \\
		\iff 0 \leq k \leq \left\lfloor \frac{t - D_i}{T_i} \right\rfloor
	\end{array}
\]
The highest value is $k = \left\lfloor \frac{t - D_i}{T_i} \right\rfloor$. If
this value is negative, it means that no job of task $\tau_i$ respects the condition, i.e.
that $h_i(t) = 0$. Else, we can inject it directly and obtain $h_i(t) =
\left\lfloor \frac{t - D_i}{T_i} \right\rfloor + 1$\\

This is generalized by the final definition of $h_i(t)$: 
\[
	h_i(t) = \operatorname{max} \{ 0, \left\lfloor \frac{t - D_i}{T_i}
	\right\rfloor + 1\}
\]

With this result, a closed form of the DBF function in the synchronous case is
obtained 
\[
	\dbf{t} = \sum_{i=1}^{n} \operatorname{max} \{ 0, \left\lfloor \frac{t -
	D_i}{T_i} \right\rfloor + 1 \} \cdot C_i
\]

@@

In \cite{baruah1990algorithms} it is shown that the DBF can be used to
derive the following feasibility condition for EDF (and thus, EDF being
optimal, for all other optimal schedulers) on sporadic task sets. An adapted
proof is given here.

\begin{theorem}
\[
	(\tau_1, ..., \tau_n) \: \text{is feasible} \iff \dbf{t} \leq t \; \forall t
\]
\end{theorem}

\begin{proof}
	We first show that the condition is \emph{necessary}. Indeed, if the condition
	is not fulfilled (i.e. $\exists t^* \; s.t. \; \dbf{t^*} > t^*$), it means that
	in an interval of $t^*$ time units, the total execution time of the jobs which
	arrival and deadline occurs within the interval is superior to $t^*$, but the
	processor can only execute $t^*$. The system is thus not feasible if the
	condition is not fulfilled.\\
